---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

##Plotly Graphs

We're going to look at the NOAA data. This data is from the National Oceanic and Atmospheric Association (NOAA) for Environmental Information(NCEI) and it provides weather data including data fro, the Global Historical Climatology Network)-Dailt database with summary statistics from weather stations worldwide.

```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```


##Loading Data
```{r}
data("ny_noaa")

ny_noaa = 
  ny_noaa %>%
  separate(date, into = c("Year", "Month", "Day"), convert = TRUE) %>%
  mutate(
    Year = as.character(Year),
    Month = as.character(Month),
    tmax = as.numeric(tmax),
    tmin = as.numeric(tmin),
    tmax = tmax / 10, 
    tmin = tmin / 10) %>%
  select(Year, Month, Day, id, tmax,tmin)%>%
  filter(
    Year == 2010,
    Day %in% 1:7) %>%
  drop_na(tmax)%>%
  drop_na(tmin)

head(ny_noaa)

```

#Plotly plots

#Scatterplot
```{r}
ny_noaa %>%
  plot_ly(
    x = ~tmax, y = ~tmin, color = ~Day,text = ~id,
    alpha = .5, type = "scatter", mode  = "markers")

```
This scatterplot shows the the maximum and minimum temperatures (tenths of degrees C) of the first seven days of each month in the 2010.



##Boxplot
```{r}
ny_noaa%>%
  mutate(Month = fct_reorder(Month, tmax))%>%
  plot_ly(
    y = ~tmax, color = ~Month,
    type = "box", colors = "viridis")
```

This boxplot shows the maximum temperatures of the first even days of each month. The y axis is the month and the y axis is the maximum temperatures.




##Barplot
```{r}
ny_noaa %>%
  count(Month) %>%
  mutate(Month = fct_reorder(Month, n)) %>%
  plot_ly(x = ~Month,y = ~n, color = ~Month, type = "bar", colors = "viridis")
```

This barplot shows the bar height and the number count of each month with month on the x axis and n being on the y axis. 

